---
title: "Generating Test Matrices"
author: "Daniel Escasa"
date: "12/28/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Once I'd written the functions, I needed matrices to test them. Two options were available to me, and I hope to others who need random matrices, not just for these functions, but for other purposes.

# Using R's built-in functions
`runif()`, among others, will do the job:
```{r}
# First make the makeCacheMatrix and cacheSolve functions available
source("cachematrix.R")
testMat <- makeCacheMatrix(matrix(runif(25), nrow = 5))
```

Then:
```{r}
testMat$get()
```
Next,
```{r}
testMat$getInv()
```
```{r}
cacheSolve(testMat)
```
```{r}
cacheSolve(testMat)
```
```{r}
testMat$getInv()
```
and, for good measure:
```{r}
testMat$get() %*% testMat$getInv()
```
Note that this doesn't look like the identity matrix. If you look more closely, however, the entries in the diagonal <strong>are</strong> ones, and the others are close enough to zero. In fact, if I had <code>round</code>'ed the matrix, the entries along the diagonal would be exactly one, and the others would be exactly zero.

I was lucky to get a non-singular matrix the first time. If <code>cacheSolve</code> returns <code>NaN</code>, you'll have to try again.

Also, you can of course pass <code>min = </code> and <code>max = </code> parameters to <code>runif</code>.

# An online random matrix generator
I found a handy site for [random generation of matrices](https://onlinemathtools.com/generate-random-matrix). 

For convenience, set the element and column separators to the comma (“,”), an option you can find below the <code>Generate Matrix</code> button. That'll make it easy to paste the generated matrix into your R console.

Here's one I got from them, plugged into the makeCacheMatrix function. Note the “byrow = true” parameter to the matrix creation function. I suppose you could omit it, giving you the transpose. Also, it doesn't always generate a non-singular matrix, so you'll have to keep at it until you get one. I used to have a program, written some 40 years ago, to generate non-singular matrices. Given enough time, I could write one again.
```{r}
testMat <- makeCacheMatrix(matrix(c(5, 4, 9, 6, 8, 1, 0, 8, 8, 3, 3, 2, 2, 9, 6, 8, 8, 8, 4, 7, 4, 8, 6, 9, 8), 
                                  nrow = 5, byrow = TRUE))
```
```{r}
testMat$get()
```
```{r}
testMat$getInv()
```
```{r}
cacheSolve(testMat)
```
```{r}
testMat$getInv()
```
```{r}
cacheSolve(testMat)
```
Verifying that this is indeed testMat's inverse is a trivial exercise for the reader.

